The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means, NN-chain for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types

### 2023-05-31 final/paper/main.tex
update paper

\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}

@@

  On the other hands, neural network classifier has another criterion. First, train a neural network that classify the 
  "konwn" and "unknown". Here "kown" means the types in train data, and "unkown" means the reverse. Then train the other 
  neural network to classify the "konwn" data. The detail is in Algo~\ref{alg:NN}.
  \begin{algorithm}[tb]
    \caption{Neural Network Classification}\label{alg:NN}
    \begin{algorithmic}[1]
      \Require $\text{Train Data, Labels, Test Data}$
      \Assume $\text{Length}(\text{Train Data})=\text{Length}(\text{Labels})=N,\text{Length}(\text{Test Data})=M$
      \State{$\text{Binary NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Mutli-Classification NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Just Knowns, Unkonwns}=\text{Binary NN}.\text{predict}(\text{Test Data})$}
      \State{$\text{Knowns}=\text{Mutli-Classification NN}.\text{predict}(\text{Just Knowns})$}
    \end{algorithmic}
  \end{algorithm}
  During the known-unknown classification, the SVDD is used. First define a model , input every data into it to get the outcome, then use the mean of the outcome as the center of the hypersphere. Then, train the model to make every data in the dataset approach to the center of the hypersphere as close as possible. After training, we can get the radius of the hypersphere, which can be define according to the outcome of the model. Using the radius, we can classify the data to "known", if the distance between the center and the data is less than or equal to the radius, or to "unknown" otherwise.

@@

  For the SVDD + NN with NN-chain, the performance is not as good as KNN, since SVDD cannot be trained with data augmented by 
  interpolation. The hypersphere that defined by SVDD includes all data points in the test dataset, which makes 
  clustering impossible. Therefore, though NN classifying achieves 100\% correctness on the known types, 
  the accuracy of SVDD + NN with NN-chain can only reach 64.45\% in gene expression cancer RNA-Seq dataset.

@@

      NN + NNChain                & $0.6338$   & $31.6456 \pm 0$                & $0.633 $   & $29.7468 \pm 0$     & $0.9358$   & $31.6456 \pm 0$      & $0.8370$   & $30.3797 \pm 0$          & $1.0540$   & $29.7468 \pm 0$      & $1.0540$   & $29.7468 \pm 0$\\

@@

      Bayes-GA + kmeans         & $2.231$    & $43.6746$         & $X$        & $X$                   & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
      NN + NNChain              & $163.359$  & $40.96   \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.96 \pm 0$            & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\

>>>>

\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means, NN-chain for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}

@@

  On the other hands, neural network classifier has another criterion. First, train a neural network that classify the 
  "konwn" and "unknown". Here "kown" means the types in train data, and "unkown" means the reverse. Then train the other 
  neural network to classify the "konwn" data. The detail is in Algo~\ref{alg:NN}.
  \begin{algorithm}[tb]
    \caption{Neural Network Classification}\label{alg:NN}
    \begin{algorithmic}[1]
      \Require $\text{Train Data, Labels, Test Data}$
      \Assume $\text{Length}(\text{Train Data})=\text{Length}(\text{Labels})=N,\text{Length}(\text{Test Data})=M$
      \State{$\text{Binary NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Mutli-Classification NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Knowns, Unkonwns}=\text{Binary NN}.\text{predict}(\text{Test Data})$}
      \State{$\text{Knowns}=\text{Mutli-Classification NN}.\text{predict}(\text{Knowns})$}
    \end{algorithmic}
  \end{algorithm}
  During the known-unknown classification, the SVDD is used. First define a model , input every data into it to get the outcome, then use the mean of the outcome as the center of the hypersphere. Then, train the model to make every data in the dataset approach to the center of the hypersphere as close as possible. After training, we can get the radius of the hypersphere, which can be define according to the outcome of the model. Using the radius, we can classify the data to "known", if the distance between the center and the data is less than or equal to the radius, or to "unknown" otherwise.

@@

  For the SVDD + NN with NN-chain, the performance is not as good as KNN, since SVDD cannot fit well with data augmented by 
  interpolation. The hypersphere that defined by SVDD includes all data points in the test dataset, which makes 
  clustering impossible. Therefore, though NN classifying achieves 100\% correctness on the known types, 
  the accuracy of SVDD + NN with NN-chain can only reach 64.45\% in gene expression cancer RNA-Seq dataset.

@@

      NN + NN-Chain               & $0.6338$   & $31.6456 \pm 0$                & $0.633 $   & $29.7468 \pm 0$     & $0.9358$   & $31.6456 \pm 0$      & $0.8370$   & $30.3797 \pm 0$          & $1.0540$   & $29.7468 \pm 0$      & $1.0540$   & $29.7468 \pm 0$\\

@@

      Bayes-GA + kmeans         & $2.231$    & $43.6746 \pm 0$   & $X$        & $X$                   & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
      NN + NN-Chain             & $163.359$  & $40.9600 \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.96 \pm 0$            & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
